\EVOSUITE at the SBST 2022 Tool Competition

### 2022-03-14 papers/sbst22/paper_sbst22.tex
Format project names with textsc

\newcommand{\JodaTime}{Joda-Time\xspace}  % That's how they write themselves -- AZ

@@

For \numTestGenFailedShort classes for \budgetShort, and \numTestGenFailedLong
classes for \budgetLong, \EVOSUITE failed to generate any tests. Unlike past
instances of the competition we found no crashes of \EVOSUITE (e.g., exceptions
thrown by \EVOSUITE) at all, but in most cases where no tests were generated
the \EVOSUITE process had been killed by the competition setup, suggesting that
\EVOSUITE was using more time than allocated. In one class of the Seata project
errors occurred during the initialisation of the target class, in which case
\EVOSUITE simply gives up since the JVM does not allow instantiation of such
classes.

While the results for line coverage and branch coverage are similar, the
mutation scores are substantially lower. The mutation scores on the Guava
classes are highest compared to the other three projects from which classes
were taken; this is surprising since Guava has been known for years to be
notoriously challenging for
\EVOSUITE~\cite{campos2015continuous,almulla2017using}. However, we find that
in many cases the mutation analysis failed because dependency classes were
missing on the classpath. While \EVOSUITE, JUnit and the coverage measurement
used in the competition apparently were able to cope with this problem anyway,
the PIT mutation analysis tool was unable to deal with this problem. This may
likely be an error in the competition setup, but it would affect all test
generation tools. While Spoon classes are affected the most, similar problems
can be observed for all projects: Considering the \budgetLong runs we found
\texttt{ClassNotFoundException}s in 414 runs for Spoon, 309 for Guava, 308 for
Fastjson, and 329 for classes in Seata; in all these cases PIT was unable to
run even when it was possible to measure coverage.

>>>>

\newcommand{\project}[1]{\textsc{#1}}
\newcommand{\Spoon}{\project{Spoon}}
\newcommand{\Guava}{\project{Guava}}
\newcommand{\Fastjson}{\project{Fastjson}}
\newcommand{\Seata}{\project{Seata}}
\newcommand{\JodaTime}{Joda-Time\xspace}  % That's how they write themselves -- AZ

@@

For \numTestGenFailedShort classes for \budgetShort, and \numTestGenFailedLong
classes for \budgetLong, \EVOSUITE failed to generate any tests. Unlike past
instances of the competition we found no crashes of \EVOSUITE (e.g., exceptions
thrown by \EVOSUITE) at all, but in most cases where no tests were generated
the \EVOSUITE process had been killed by the competition setup, suggesting that
\EVOSUITE was using more time than allocated. In one class of the \Seata project
errors occurred during the initialisation of the target class, in which case
\EVOSUITE simply gives up since the JVM does not allow instantiation of such
classes.

While the results for line coverage and branch coverage are similar, the
mutation scores are substantially lower. The mutation scores on the \Guava
classes are highest compared to the other three projects from which classes
were taken; this is surprising since \Guava has been known for years to be
notoriously challenging for
\EVOSUITE~\cite{campos2015continuous,almulla2017using}. However, we find that
in many cases the mutation analysis failed because dependency classes were
missing on the classpath. While \EVOSUITE, JUnit and the coverage measurement
used in the competition apparently were able to cope with this problem anyway,
the PIT mutation analysis tool was unable to deal with this problem. This may
likely be an error in the competition setup, but it would affect all test
generation tools. While \Spoon classes are affected the most, similar problems
can be observed for all projects: Considering the \budgetLong runs we found
\texttt{ClassNotFoundException}s in 414 runs for \Spoon, 309 for \Guava, 308 for
\Fastjson, and 329 for classes in \Seata; in all these cases PIT was unable to
run even when it was possible to measure coverage.
